Finally, a functional class scoring method for enrichment analysis of Infinium DNA methylation data

### 2023-12-09 figs/GSE158422_rna_int.Rmd
fig5

suppressPackageStartupMessages({
  library("DESeq2")
  library("eulerr")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylationEPICanno.ilm10b4.hg19")
  library("tictoc")
  library("limma")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("missMethyl")
  library("HGNChelper")
  library("gplots")
})

@@

@@

@@

>>>>

suppressPackageStartupMessages({
  library("DESeq2")
  library("eulerr")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylationEPICanno.ilm10b4.hg19")
  library("tictoc")
  library("limma")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("missMethyl")
  library("HGNChelper")
  library("gplots")
  library("gridExtra")
  library("png")
})

@@

pdf("fig5c.pdf")
heatmap.2( as.matrix(mtop) , trace="none",margins = c(6,25), col=colfunc(25), cexRow=.6, cexCol=1)
dev.off()

@@

pdf("fig5a.pdf")
plot(euler(vg),quantities=TRUE)
dev.off()

@@

pdf("fig5b.pdf")
plot(euler(vm),quantities=TRUE)
dev.off()

### 2023-12-09 manuscript/manuscript.Rmd
fig5

>>>>

![Figure 5. Integration of gene expression data with methylation pathways. (A,B) Euler diagrams showing the overlap in statistically significant pathways (FDR<0.05) from gene expression and GSA results (A) and LAM (B) results. (C) Multi-dimensional enrichment analysis of promoter and gene body methylation with gene expression using mitch. Top 20 gene sets shown with largest s distance after FDR siltering at 0.05.](../figs/fig5.png)
